Modal Verification Patterns for Systems

### 2025-06-23 paper.tex
+

Like VMMs navigating between different address-spaces, a \textsf{CoW} filesystem switches from either the old to the new root yields consistent views of the filesystem at different points in time, each commonly referred to as a \emph{snapshot}.
These snapshots overlap on the unmodified portions of the filesystem (the left-most grid section), with the reclaimed the chunks (the middle gray section) becoming available for reuse once the new snapshot becomes the official current state of the filesystem.\footnote{Many of these filesystems permit keeping archived snapshots of the filesystem state, e.g., a snapshot of the system every hour up to a certain number of days, to support user data recovery. In these cases only disk regions that are not still in use by an archived snapshot are reclaimed.}. This permits the filesystem to atomically switch between consistent on-disk states, by updating the oldest so-called \emph{super} chunk at a fixed location on disk.\footnote{Filesystems must take care to ensure that possibly-flaky hardware truly does perform an atomic update.} Super chunks, as we see in Figure \ref{fig:cowindex} as ($\textsf{Super}_0$ and $\textsf{Super}_1$), are the first two blocks of the disk dedicated to keep the state of the file system which is composed of some meta-data on the filesystem, and most importantly to the root chunk of the file system index-tree. Therefore, in case of a crash during the update to the \textsf{file "foo"}, we can reboot the file system from the previous persisted root, \textsf{root chunk}, via reading the $\textsf{Super}_0$. This means the whole disk consistency checks are unnecessary when recovering from a crash~\cite{bonwick2003zettabyte,hitz1994file}; recovery is immediate, as opposed to requiring hours or days~\cite{henson2006reducing,agrawal2009speedy} (or longer~\cite{henson2006chunkfs}) for recovering a large volume’s consistency from logs. 
An important additional subtlety with this kind of filesystem is \emph{when} blocks in the reclaimed region can actually be reused: only \emph{after} the snapshot that made those blocks ``free'' has been completely written to disk. Allowing reuse before this could result in in-place updates: part of the new snapshot could attempt to store data in space used by the prior snapshot, allowing inconsistent on-disk structures. 
\begin{figure}
    \includegraphics[width=\columnwidth]{journalling.png}
    \caption{A Filesystem Utilizing \emph{Journalling} for Consistent Disk-Layout ~\cite{chajed2021gojournal}}
    \label{fig:journal}
\end{figure}

>>>>

Like VMMs navigating between different address-spaces, a \textsf{CoW} filesystem switches from either the old to the new root yields consistent views of the filesystem at different points in time, each commonly referred to as a \emph{snapshot}. Like VMMs 
These snapshots overlap on the unmodified portions of the filesystem (the left-most grid section), with the reclaimed the chunks (the middle gray section) becoming available for reuse once the new snapshot becomes the official current state of the filesystem. This permits the filesystem to atomically switch between consistent on-disk states, by updating the oldest so-called \emph{super} chunk at a fixed location on disk. Super chunks, as we see in Figure \ref{fig:cowindex} as ($\textsf{Super}_0$ and $\textsf{Super}_1$), are the first two blocks of the disk dedicated to keep the state of the file system which is composed of some meta-data on the filesystem, and most importantly to the root chunk of the file system index-tree. Therefore, in case of a crash during the update to the \textsf{file "foo"}, we can reboot the file system from the previous persisted root, \textsf{root chunk}, via reading the $\textsf{Super}_0$. This means the whole disk consistency checks are unnecessary when recovering from a crash~\cite{bonwick2003zettabyte,hitz1994file}; recovery is immediate, as opposed to requiring hours or days~\cite{henson2006reducing,agrawal2009speedy} (or longer~\cite{henson2006chunkfs}) for recovering a large volume’s consistency from logs. 
An important additional subtlety with this kind of filesystem is \emph{when} blocks in the reclaimed region can actually be reused: only \emph{after} the snapshot that made those blocks ``free'' has been completely written to disk. Allowing reuse before this could result in in-place updates: part of the new snapshot could attempt to store data in space used by the prior snapshot, allowing inconsistent on-disk structures. 
\begin{figure}
    \includegraphics[width=\columnwidth]{journalling.png}
    \caption{A Filesystem Utilizing \emph{Journalling} for Consistent Disk-Layout ~\cite{chajed2021gojournal}}
    \label{fig:journal}
\end{figure}
